Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-14 main.tex
New try

A {\em contoured trace} is a finite or infinite sequence
$\seq{(\contour,\mach)} = (\contour_0,\mach_0),\,
(\contour_1,\mach_1),\ldots$ of (contour, machine state) pairs.

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = (\LOW$,\,\underscore), then
$\mach(\component) = \mach'(\component)$.

@@

Formally, $\obstrace(\seq{(\contour,\mach)})$ can be constructed as
follows. For each component $\component$,
%
if
$\contour_i(\component) = (\underscore,\HIDDEN)$ for all $i$, then
$\obstrace(\component) = \bot$;
%
otherwise, $\obstrace(\component)$ is a sequence whose first element
is $\mach_i(\component)$ for the smallest $i$ such that
$\contour_i(\component) = (\underscore,\OBS)$ and whose $(m+1)^{th}$ element
(if any) is $\mach_j(\component)$, where $j$ is the smallest index greater
than the index $i$ of the $m^{th}$ element and such that
$\contour_j(\component) = (\underscore,\OBS)$ and
$\mach_j(\component) \neq \mach_i(\component)$.
%
\iftext
\bcp{Unfinished and horrible...  But maybe the textual description is OK?}
\newcommand{\aux}{\mathit{aux}}
\bcp{Don't like the ``rest'' argument and the fact that we don't
  have a metavariable for sequences of (contour, machine state) pairs.
  Consider defining one.}
%
\[
\begin{array}{lcl}
\aux \; ( [\,] ) \; \trace& = & \trace
\\
\aux \; ( (\contour,\mach) \mathrel{::} \mathit{rest} ) \; T
  & = &
        \aux \;( \mathit{rest} )
        \\ && \quad (\lambda k.\; \mbox{\bcp{and so on}}
\\
\\
\obstrace \;( (\contour_0,\mach_0),\, \ldots )
  &=& \aux \; ( (\contour_0,\mach_0),\, \ldots ) \; (\lambda
      \component.\, \bot)
\end{array}
\]
\fi

@@

@@

Policy $\pol$ {\em guarantees} property $\prop$ if \bcp{......}

@@

If $\mach$ and $\mach'$ are variant machine states with respect to contour
$\contour$, then $\mach$ and $\mach'$ are said to be {\em indistinguishable}
under policy $\pol$ if their observable
%
$\obstrace(
                      (\contour,\mach)
  \stepstounder{\pol} (\contour_1,\mach_1)
  \stepstounder{\pol} (\contour_2,\mach_2)
  \stepstounder{\pol} \ldots)$
%
yields the same trace as
$\obstrace(
                      (\contour,\mach')
  \stepstounder{\pol} (\contour_1,\mach_1')
  \stepstounder{\pol} (\contour_2,\mach_2')
  \stepstounder{\pol} \ldots)$.

% either (1) one or both of $(\contour,\mach)$ and
% $(\contour,\mach')$ fail to terminate when executed with
% $\stepstounder{\pol}$, or (2) both terminate and the machine-state
% components of their results are variants with respect to the original
% $\contour$.

@@

\section{Tainting is noninterference$-$}

>>>>

A {\em contoured trace} is a finite or infinite sequence
$\seq{(\contour,\mach)} = (\contour_0,\mach_0),\,
(\contour_1,\mach_1),\ldots$ of (contour, machine state) pairs \bcp{such
  that the machine parts agree with the full step}.

Given a machine state $\mach$ and a contour $\contour$, a {\em variant} of
$\mach$ with respect to $\contour$ is any machine state $\mach'$ whose
components agree with $\mach$ on all components marked $\LOW$ by
$\contour$---i.e., if $\contour(\component) = (\LOW$,\,\underscore), then
$\mach(\component) = \mach'(\component)$.  \bcp{Move this to the NI section.}

@@

Formally, $\obstrace(\seq{(\contour,\mach)})$ can be constructed as
follows. For each component $\component$,
%
if
$\contour_i(\component) = (\underscore,\HIDDEN)$ for all $i$, then
$\obstrace(\component) = [\,]$;
%
otherwise, $\obstrace(\component)$ is a sequence whose first element
is $\mach_i(\component)$ for the smallest $i$ such that
$\contour_i(\component) = (\underscore,\OBS)$ and whose $(m+1)^{th}$ element
(if any) is $\mach_j(\component)$, where $j$ is the smallest index greater
than the index $i$ of the $m^{th}$ element and such that
$\contour_j(\component) = (\underscore,\OBS)$ and
$\mach_j(\component) \neq \mach_i(\component)$.
%
\bcp{Can be defined more simply}
\iftext
\bcp{Unfinished and horrible...  But maybe the textual description is OK?}
\newcommand{\aux}{\mathit{aux}}
\bcp{Don't like the ``rest'' argument and the fact that we don't
  have a metavariable for sequences of (contour, machine state) pairs.
  Consider defining one.}
%
\[
\begin{array}{lcl}
\aux \; ( [\,] ) \; \trace& = & \trace
\\
\aux \; ( (\contour,\mach) \mathrel{::} \mathit{rest} ) \; T
  & = &
        \aux \;( \mathit{rest} )
        \\ && \quad (\lambda k.\; \mbox{\bcp{and so on}}
\\
\\
\obstrace \;( (\contour_0,\mach_0),\, \ldots )
  &=& \aux \; ( (\contour_0,\mach_0),\, \ldots ) \; (\lambda
      \component.\, \bot)
\end{array}
\]
\fi

\bcp{Maybe make it a sequence of maps from components to values?  This is
  simpler, but it means we can ``observe the observbility of locations...''
But is this too unrealistic?}

@@

\bcp{NI is the property where:
  \begin{itemize}
  \item In each top-level pair (each element of the hyperproperty), all the
  contours coincide.
  \item If the initial machine states plus contour are variants, then the
  observervations of the two traces coincide.
  \end{itemize}
}

% If $\mach$ and $\mach'$ are variant machine states with respect to contour
% $\contour$, then $\mach$ and $\mach'$ are said to be {\em indistinguishable}
% under policy $\pol$ if their observable
% %
% $\obstrace(
%                       (\contour,\mach)
%   \stepstounder{\pol} (\contour_1,\mach_1)
%   \stepstounder{\pol} (\contour_2,\mach_2)
%   \stepstounder{\pol} \ldots)$
% %
% yields the same trace as
% $\obstrace(
%                       (\contour,\mach')
%   \stepstounder{\pol} (\contour_1,\mach_1')
%   \stepstounder{\pol} (\contour_2,\mach_2')
%   \stepstounder{\pol} \ldots)$.

% % either (1) one or both of $(\contour,\mach)$ and
% % $(\contour,\mach')$ fail to terminate when executed with
% % $\stepstounder{\pol}$, or (2) both terminate and the machine-state
% % components of their results are variants with respect to the original
% % $\contour$.

@@

Policy $\pol$ {\em guarantees} property $\prop$ if \bcp{for every pair of
  starting states and every starting contour, the pair of traces that you
  get from the policy is in the property for {\em some} pair of sequences of
  contours that agree with the given contour on the first element.}

@@

@@

\newpage
\section{Tainting is noninterference$-$}
